\documentclass[letterpaper,10.5pt]{article}
% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

\begin{document}

%---------- HEADING ----------
\begin{center}
    {\Huge \textbf{Mostafa Ashraf Mostafa}} \\ \vspace{5pt}
    \small
    \href{mailto:mostafafergany28@gmail.com}{mostafafergany28@gmail.com} 
    $|$ New Cairo
    $|$ 01096154975
    $|$ \href{https://www.linkedin.com/in/mostafa-ashraf-074792324}{LinkedIn: mostafa-ashraf-074792324}
    $|$ \href{https://github.com/mostafaashraff28}{GitHub: mostafaashraff28}
\end{center}

%----------- EDUCATION -----------
\section{Education}
\textbf{Arab Academy for Science, Technology and Maritime Transport (AAST)} \hfill Cairo, Egypt \\
\textit{B.Sc. in Computer Engineering} \hfill \textbf{GPA: 3.3/4.00} \\
\textit{Sep 2020 -- June 2025}

%----------- EXPERIENCE -----------
\section{Experience}
\textbf{Flutter Developer Intern} \hfill \textit{Information Technology Institute (ITI)} \\
\textit{Aug 2023 -- Sep 2023} \\
\begin{itemize}[leftmargin=*]
    \item Developed mobile applications using Flutter and Dart.
    \item Final project: Designed and built a \textbf{Netflix Clone} app using Firebase.
\end{itemize}

\textbf{Information Technology Intern} \hfill \textit{Arab Investment Bank (AIB)} \\
\textit{Jul 2023 -- Aug 2023} \\
\begin{itemize}[leftmargin=*]
    \item Gained hands-on experience in software development, communication, and teamwork.
    \item Worked with the IT team to optimize digital banking solutions.
\end{itemize}

%----------- SKILLS -----------
\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming:} Python, C/C++, Java, Dart, MySQL, Bash Scripting
    \item \textbf{DevOps Tools:} Docker, Git/GitHub Actions, Cloud Computing (AWS/GCP)
    \item \textbf{Networking:} Routing \& Switching (Cisco Packet Tracer)
    \item \textbf{Software Development:} SDLC, Microservices Architecture
\end{itemize}

\section{Soft Skills}
\begin{itemize}[leftmargin=*]
    \item Strong communication, teamwork, and leadership abilities
    \item Problem-solving and analytical thinking
\end{itemize}

%----------- CERTIFICATIONS -----------
\section{Certifications}
\begin{itemize}[leftmargin=*]
    \item \textbf{Flutter Developer} – Information Technology Institute (ITI)
    \item \textbf{Information Technology} – Arab Investment Bank (AIB)
\end{itemize}

%----------- COURSES -----------
\section{Relevant Courses}
\begin{itemize}[leftmargin=*]
    \item \textbf{100 Days of Code: The Complete Python Pro Bootcamp} – Udemy
    \item \textbf{Flutter \& Dart \& Firebase Complete Development Course} – Udemy
    \item \textbf{Cisco Packet Tracer Training} – University
    \item \textbf{Neural Networks \& AI Models} – University
\end{itemize}

%----------- PROJECTS -----------
\section{Projects}
\textbf{Netflix Clone} \hfill \textit{Flutter, Dart, Firebase} \\
\textit{2023} \\
\begin{itemize}[leftmargin=*]
    \item Designed and implemented a Netflix-inspired streaming platform using Flutter.
    \item Integrated Firebase for authentication and real-time data storage.
\end{itemize}

\textbf{AI-Based Chatbot} \hfill \textit{Python, NLP, Machine Learning} \\
\textit{2022} \\
\begin{itemize}[leftmargin=*]
    \item Developed an AI chatbot using Natural Language Processing (NLP).
    \item Trained the model with machine learning techniques to improve response accuracy.
\end{itemize}

\end{document}
